TBD

### 2016-10-11 paper.tex
added more text to the conjugate gradient section

The Conjugate Gradient method was independently discovered by Hestenes and Stiefel. They later published a joint paper, n, which is now considered as the seminal
reference on CG. Kaniel was able to determined convergence bounds for CG using Chebyshev polynomial. A much more in depth analysis of CG convergence was conducted 
by van erSluis and van der Vorst. Reid is credited for popularizing CG as an iterative method that can be used to solve sparse linear systems.

In the early fifties, the method of Conjugate Gradients
was discovered independently by Hestenes [10] and Stiefel [15]; shortly thereafter, they jointly published
what is considered the seminal reference on CG [11]. Convergence bounds for CG in terms of Chebyshev
polynomials were developed by Kaniel [12]. A more thorough analysis of CG convergence is provided by
van der Sluis and van der Vorst [16]. CG was popularized as an iterative method for large, sparse matrices
by Reid [13] in 1971.

\begin{algorithm}
\caption{Conjugate Gradient Method}\label{algo:extrap_algo}
\begin{algorithmic}[1]
\State $\br_0 \gets \bA\bx_0 - \bb$
\State $\bp_0 \gets -\br_0$
\State $\bmath{u} \gets \text{linspace}(u_{\text{min}},u_{\text{max}},u_{\text{dim}})$
\State $\bmath{v} \gets \text{linspace}(v_{\text{min}},v_{\text{max}},v_{\text{dim}})$ 
\State $g_{pq} \gets \text{zeros}((u_{\text{dim}},v_{\text{dim}}),\text{dtype}=\text{complex})$ \Comment {define your 2D extrapolated regular $uv$-grid}
\State $i \gets 1$
\For{$i\leq u_{\text{dim}}$}  
\State $j \gets 1$
\For{$j\leq v_{\text{dim}}$}  
\State $\bb \gets (\bmath{u}_i,\bmath{v}_j)^T$
%\State $\Rcal \gets \left\{ \sum_{k\in\mathcal{K}}A_k e^{-2\pi i [\widehat{X}_{rs} \circ \widehat{X}^{-1}_{pq}(\bb)]^T\cdot\bs_k} \right \}_{rs}$
%\State $\Mcal \gets \left\{ \sum_{h\in\mathcal{H}}A_h e^{-2\pi i [\widehat{X}_{rs} \circ \widehat{X}^{-1}_{pq}(\bb)]^T\cdot\bs_h} \right \}_{rs}$
%\Comment {with $\mathcal{K}$ containing the index values of all the sources in the field of view and $\mathcal{L}$ containing the index values of the sources that are included in the
%calibration model}
%\State $\Gcal \gets \text{calibrate}(\Rcal,\Mcal)$
%\Comment {any calibration algorithm can be used here (we assume here that the algorithm outputs $\Gcal$)}
%\State $g_{pq}^{ij} \gets [\Gcal]_{pq}$
\State $j \gets j + 1$
\EndFor
\State $i \gets i + 1$
\EndFor
\end{algorithmic}
\end{algorithm}

>>>>

The Conjugate Gradient method was independently discovered by Hestenes and Stiefel. They later published a joint paper, n, which is now considered as the seminal
reference on CG. Kaniel was able to determine convergence bounds for CG using Chebyshev polynomials. A much more in depth analysis of CG convergence was conducted 
by van erSluis and van der Vorst. [Reid is credited for popularizing CG as an iterative method that can efficiently solve large sparse linear systems] RW.

\begin{algorithm}
\caption{Conjugate Gradient Method}\label{algo:extrap_algo}
\begin{algorithmic}[1]
\State $\br \gets \bA\bx_0 - \bb$
\State $\bp \gets -\br_0$
\For{$k\leq k_{\textrm{max}}$}
\State $\alpha_k \gets \frac{\br_k^H\br_k}{\bp_k^H\bA\bp_k}$
\State $\bx_{k+1} \gets \bx_k + \alpha_k\bp_k$
\State $\br_{k+1} \gets \br_k - \alpha_k\bA\bp_k$
\If{$\|\br_{k+1}\|<\epsilon\|\br_0\|$}
\State break
\EndIf
\State $\beta_{k} \gets \frac{\br_{k+1}^H\br_{k+1}}{\br_k^H\br_k}$
\State $\bp_{k+1} \gets \br_{k+1} + \beta_{k}\bp_k$
\State $k \gets k + 1$
\EndFor
\end{algorithmic}
\end{algorithm}

In general, when $\bA$ is neither square, positive semi-definite or Hermitian we can use the normal equation 
\begin{equation}
\label{eq:normal_equation}
\bA^H\bA\bx = \bA^H\bb 
\end{equation}
to estimate the $\bx$ that minimizes
\begin{equation}
\|\bb-\bA\bx\|. 
\end{equation}
The CG method is gaurenteed to converge if we use it to solve Eq.~\eqref{eq:normal_equation}.
